---
title: "Live Session Assignment 6"
author: "Chris Irwin"
date: "10/15/2016"
output: html_document
---

Please load the following packages (plyr, gdata)
```{r include=FALSE}
require(plyr)
require(gdata)
```

After downloading the Excel file and saving it as a .csv file run the following command
```{r}
qns <- read.csv("rollingsales_Queens.csv",skip=4,header=TRUE)
```

We need to remove commas from the data set, we will create a new column named Sale.Price.N
```{r}
qns$SALE.PRICE.N <- as.numeric(gsub("[^[:digit:]]","", qns$SALE.PRICE))
```

See the number of records that have an NA after removing commas
```{r}
count(is.na(qns$SALE.PRICE.N))
```

We are renaming the variables names to be all lower case
```{r}
names(qns) <- tolower(names(qns))
head(qns)
```

Remove additional commas in columns gross.sqft, land.sqft
```{r}
qns$gross.sqft <- as.numeric(gsub("[^[:digit:]]","", qns$gross.square.feet))
qns$land.sqft <- as.numeric(gsub("[^[:digit:]]","", qns$land.square.feet))
```

Cast year.built as numeric
```{r}
qns$year.built <- as.numeric(as.character(qns$year.built))
```

Look at price data to see if there are any outliers
```{r}
hist(qns$sale.price.n) 
```

When looking at the histogram we see there are some very large outliers. We want to remove any sale that do not have an actual sales price.  
```{r}
qns.sale <- qns[qns$sale.price.n!=0,]
dim(qns.sale)
```

Create a plot to show Gross SQ Ft vs Sales Price  
```{r}
plot(qns.sale$gross.sqft,qns.sale$sale.price.n)
```

Due to the extreme outliers we can try a log transformation 
```{r}
plot(log10(qns.sale$gross.sqft),log10(qns.sale$sale.price.n))
```

Now we want to look at 1, 2 and 3 family homes
```{r}
qns.homes <- qns.sale[which(grepl("FAMILY",qns.sale$building.class.category)),]
dim(qns.homes)
plot(log10(qns.homes$gross.sqft),log10(qns.homes$sale.price.n))
```

Take a look at the summary for sales prices of family homes lower than 100,000.00
```{r}
summary(qns.homes[which(qns.homes$sale.price.n<100000),])
```

We want to remove any outliers that look like they werent actual sales. We created a new column called outliers by using the log of 10. 
```{r}
qns.homes$outliers <- (log10(qns.homes$sale.price.n) <=5) + 0
```

Now we want to remove the outliers and only use properties that are sales by recreating the qns.homes data set. 
```{r}
qns.homes <- qns.homes[which(qns.homes$outliers==0),]
```

Final Tidy data set 
```{r}
plot(log(qns.homes$gross.sqft),log(qns.homes$sale.price.n))
```

Create additional Graphs for Analysis
```{r}
library(plotly)
library(sqldf)
average.PricePerHood <- sqldf('select neighborhood, avg([sale.price.n]) as AverageOfHood from [qns.homes] group by neighborhood order by neighborhood')

 plot_ly(x = average.PricePerHood$neighborhood, y= average.PricePerHood$AverageOfHood, Name = "Average Price per Neighborhood", type = "bar")

```







